Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-06 article.rnw
Read the brute force output into the article's R code.
Add the species names to the article's R code.
Add a helper script for post-processing the brute force data.
Add a post processing function to validate the data.
Rewrite the brute force post processing code using R6.
Add a note to methods, justifying the use of normal likelihood.

@@

>>>>

<<include=FALSE>>=
	source("r/brute-post-process.R")
	brute_data <- BruteData$new(
		"output/brute.data",
		c(
			"D. birchii",
			"D. pallidifrons",
			"D. pandora",
			"D. pseudoananassae",
			"D. simulans",
			"D. sulfurigaster"
		)
	)
@

@@

\section{Methods}

\subsection{Model fitting}

The model was fitted by least squares regression, with a normal likelihood.\footnote{
	I recognise that this is erroneous, and a likelihood directly suited to count data would be more appropriate.
	The choice to fit the Lotka--Volterra model specifically, rather than a generic regression model, prohibited the use of a link function.
	This prevented me from using the typical methods of generalised nonlinear regression, and I have not yet managed to develop the methods necessary to fit the model using a Poisson or negative binomial likelihood.
}
